\textbf{{\Large {Recursive algorithm for the computation of branching coefficients of affine Lie algebras with applications in CFT}}}

### 2009-12-17 AffineLieAlgebras/InformalNotes/article.tex
More work on special embeddings. Simplier example of conformal embedding is proposed.

All the cases are listed in the table \ref{tab:diagrams}.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\  
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}
In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.

@@

@@

Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first to components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.

@@

>>>>

All the cases are listed in the table \ref{tab:diagrams}.
\begin{table}[ph]
\label{tab:diagrams}
\noindent  \centering{
\begin{tabular}{|l|l|l|l|}
  \hline
  $\mathfrak{g}$ & Extended diagram of the algebra $\mathfrak{g}$ & Diagrams of the subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ \\
  \hline
  $A_n$ & \includegraphics{A_series_ext_diag.pdf} & \includegraphics{A_series_ext_split.pdf} \\
  \hline
  $B_n$ & \includegraphics{B_series_ext_diag.pdf} & \includegraphics{B_series_ext_split.pdf} \\  
  \hline
  $C_n$ & \includegraphics{C_series_ext_diag.pdf} & \includegraphics{C_series_ext_split.pdf} \\
  \hline
  $D_n$ & \includegraphics{D_series_ext_diag.pdf} & \includegraphics{D_series_ext_split.pdf} \\
  \hline
\end{tabular}
\caption{Subalgebras $\mathfrak{a},\; \mathfrak{a}_{\bot}$ for the classical series}}
\end{table}

The exceptional Lie algebras require tedious case-by-case analysis.

In the language of Weyl groups the task of construction of the root system of $\mathfrak{a}_{\bot}$ is formulated as follows. Given a Weyl group $W$ and a subgroup $W_{\mathfrak{a}}$ find the subgroup $W_{\mathfrak{a}_{\bot}}\subset W$ such that $\omega\, W_{\mathfrak{a}}\,\omega^{-1}=W_{\mathfrak{a}}; \;\text{for}\; \omega\in W_{\mathfrak{a}_{\bot}}$, so we need to find the normalizer of $W_{\mathfrak{a}}$ in $W$, such that some of the elements of $W_{\mathfrak{a}_{\bot}}$ are the reflections corresponding to the positive roots of $\mathfrak{g}$. This task can be carried out using the computational methods of finite group theory \cite{stembridge2001computational} but we are unaware of any publication with the exhaustive tables of such a subgroups.

@@

Using the existing classification of maximal special subalgebras \cite{dynkin1952semisimple} we immediately have the following pairs of the orthogonal subalgebras $\mathfrak{a},\;\mathfrak{a}_{\bot}$ 
\begin{equation}
  \label{eq:42}
  \begin{array}{lll}
      su(p)\oplus su(q) & \subset su(pq) &\\
      so(p)\oplus so(q) & \subset so(pq) &\\
      sp(2p)\oplus sp(2q) & \subset so(4pq)&\\
      sp(2p)\oplus so(q) & \subset sp(2pq)&\\
      so(p)\oplus so(q) & \subset so(p+q)& \text{for}\;p\;\text{and}\;q\;\text{odd}\\
  \end{array}
\end{equation}
Exceptional Lie algebras and other non-maximal subalgebras require lengthy analysis which is not important for the needs of computation of the branching coefficients.

@@

Consider the level one representation of the algebra $\mathfrak{g}=\hat{B_2}$ with the highest weight $w_1=(1,0,1,0)$, where the first two components are the coordinates of the classical part in the orthogonal basis $e_1,e_2$, the third is the grade of the weight and the fourth is the level.

@@

\subsubsection{Special embedding $\hat{A}_1\subset\hat{A}_2$}
\label{sec:spec-embedd-hata_1s}
Consider the embedding of the affine Lie algebra $\hat{A}_1$ into $\hat{A}_2$ built as the affine extension of the special embedding $su(2)\subset su(3)$ with the embedding index $x_e=4$. The level of the algebra $\mathfrak{g}=\hat{A}_2$ is equal to one, so the level of the subalgebra $\tilde{k}=kx_e=4$.

\begin{enumerate}
\item Construct the set $\Delta^{+}$ of the positive roots of the algebra $\mathfrak{g}$.
\item Select the positive roots $\alpha\in \Delta^{+}$ which are orthogonal to the root subspace of the subalgebra $\mathfrak{a}$ and form the set $\Delta^{+}_{\bot}$.
\item Construct the set $\widehat{\Psi^{(\mu)}}=\left\{\omega(\mu+\rho)-\rho;\; \omega\in W\right\}$ of the anomalous points of the $\mathfrak{g}$-module $L^{(\mu)}$.
\item Select those weights $\lambda=\omega(\mu+\rho)$ which lies in the closure of the main Weyl chamber of the algebra $\mathfrak{a}_{\bot}$. Since we have constructed the set $\Delta^{+}_{\bot}$ we can easily check if the weight $\lambda$ lies in the main Weyl chamber of $\mathfrak{a}_{\bot}$ checking that the scalar product of $\lambda$ with the roots of $\Delta^{+}_{\bot}$ is non-negative.
\item For $\lambda=\omega(\mu+\rho),\; \lambda\in \bar{C}_{\mathfrak{a}_{\bot}}$ calculate the dimensions of the corresponding modules $\mathrm{dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right)$ using the Weyl formula with the set $\Delta^{+}_{\bot}$.
\item Construct the set $\Gamma$ \eqref{fan-defined}.
\item Calculate anomalous branching coefficients in the main Weyl
  chamber of the subalgebra $\mathfrak{a}$ using recurrent relation (\ref{recurrent relation}).
\end{enumerate}

There exist three level one dominant weights $[1,0,0],\;[0,1,0],\;[0,0,1]$ in the weight space of $\hat{A}_2$.
It is easy to see that the set $\Delta_{\bot}$ is trivial. 
\subsubsection{Special embedding $\hat{su}(2)\subset \hat{sp}(4)$.}
\label{sec:spec-embedd-wideh}
